---
title: "Aides Drug"
author: "Glen Abram"
date: "10/30/2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. We will conduct an evaluation of drug efficacy for everyone.We will then conduct an evaluation of drug efficacy for females only.Thirdly, we will conduct an evaluation of drug efficacy for males only.Moreover, we will execute an evaluation of drug efficacy for only drug users. Finally, an evaluation of drug efficacy for only LBGTQ.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

For each of the five tests, the ressponse is categorical, The factor variable is categorical so we...

## Question 1: Is the vaccine effective for the population?
$H_0$ The vaccine has no effect on whether one contracts aids or not
$H_1$ The vaccine affects whether one contracts aids or not

## Question 2: Is the vaccine effective for gals?
$H_0$ The vaccine has no effect on whether gals contracts aids or not
$H_1$ The vaccine affects whether gals contracts aids or not

## Question 3: Is the vaccine effective for guys?
$H_0$ The vaccine has no effect on whether guys contracts aids or not
$H_1$ The vaccine affects whether guys contracts aids or not

## Question 4: Is the vaccine effective for drug users?
$H_0$ The vaccine has no effect on whether drug users contracts aids or not
$H_1$ The vaccine affects whether drug users contracts aids or not

## Question 5: Is the vaccine effective LGBQT?
$H_0$ The vaccine has no effect on whether LGBQT contracts aids or not
$H_1$ The vaccine affects whether LGBQT contracts aids or not

This barchart depicts aids patients that consumed the placebo had a higher percentage than those that consumed the drug. Nonetheless, People without the virus were close in percentages.

```{r}
allPeople = xtabs(~infected + treatment, data = avast)
rowPerc(allPeople)

```
```{r}
chisqtestGC(allPeople,data=avast)
```

This table shows the p value is 0 which is less than 0.05. Therefore we reject the null hypothesis. It shows that the drug is more effective than the placebo.







#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC( ~ infected+treatment, type='percent', main= 'ENTIRE POP.', horizontal = TRUE, data=avast)
```
This barchart depicts the whole population with aids and without aids is affected or not affected with the drug. The pink displays how much the drug counteracted the aids virus as opposed to the placebo for people with aids. For people without aids the pink and blue are very closein rangebecause they do not have the aids virus. Ifb they were not close in range then that would mean something is wrong with this study.

```{r}
barchartGC(~infected + treatment, data = avast,type='percent')
```

```{r}
barchartGC(~infected + treatment, data = filter(avast, sex == 'gal') , main='Women only', type='percent')
```
This barchart depicts that the drug is effective for women/gals contracting aids.

```{r}
barchartGC(~infected + treatment, data = filter(avast, sex == 'guy') , main='men only', type='percent')
```
This barchart depicts that guys with aids virus should not take the drug because it makes them more susceptible to contracting the aids virus

```{r}
barchartGC(~ infected+treatment, , main = 'DrugUser', type ='percent', data=filter(avast, DrugUser == 'yes'), horizontal = TRUE) 
```
This barchart depicts people who are drug users and take the drug to prevent aids the results are far more effective than drug users who take theplacebo. We can also see people who don'thave aids that use the placebo and the drug are close in range.

```{r}
barchartGC(~ infected+treatment, , main = 'LGBTQ', type ='percent', data=filter(avast, LGBTQ == 'gay'), horizontal = TRUE) 
```
This barchart displays people in the LGBTQ group who already have aids, should not takethe drug because it made them more susceptible to getting aids.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
tab1 = xtabs (~infected+treatment, data=filter(avast))
rowPerc(tab1)
```

```{r}
tab2 = xtabs (~infected+treatment, data=filter(avast,sex== 'gal' ))
rowPerc(tab2)
```

```{r}
tab3 = xtabs (~infected+treatment,data=filter(avast,sex== 'guy' ))
rowPerc(tab3)
```

```{r}
tab4 = xtabs (~infected+treatment,data=filter(avast,DrugUser== 'yes' ))
rowPerc(tab4)
```

```{r}
tab5 = xtabs (~infected+treatment,data=filter(avast,LGBTQ== 'gay' ))
rowPerc(tab5)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
